### 2015-06-07 chapters/pitfalls.tex
adding section summary to chapter 2

Together with the topic of normalization (NFC vs.~NFD, see 
Section~\ref{pitfall-canonical-equivalence} above),
this leads to the following nicely cryptic file-encoding recommendation, namely
to preferably use UTF-8 in NFC without BOM with LF line breaks,
whenever possible.

>>>>

Summerizing the pitfalls discussed in this chapter, we propose the following 
recommendations:

\begin{itemize}
   \item To prevent strange boxes instead of nice glyphs, always install a few
         fonts with a large glyph collection and at least one fall-back font
         (see Section~\ref{pitfall-missing-glyphs}).
   \item Unexpected visual impressions of symbols does not necessarily mean that
         the actual encoding is wrong. It is mostly a problem of faulty
         rendering (see Section~\ref{pitfall-faulty-rendering}).
   \item Do not trust the names of Unicode blocks as a strategy to find specific 
         characters (see Section~\ref{pitfall-blocks})
   \item To ensure consistent encoding of texts, apply Unicode normalization
         (NFC or NFD, see Section~\ref{pitfall-canonical-equivalence}).
   \item To prevent remaining inconsistencies after normalization, for example 
         stemming from homoglyphs (see Section~\ref{pitfall-homoglyphs}) 
         or from missing canonical equivalence in the Unicode Standard
         (see Section~\ref{pitfall-absence-of-equivalence})
         use orthography profiles (see Chapter~\ref{orthography-profiles}).
   \item As a preferred file format, use UTF-8 in NFC without BOM with 
         LF line breaks, whenever possible (see 
         Section~\ref{pitfall-file-formats}). This nicely cryptic recommendation 
         has the T-shirt potential:

\begin{center}
  I prefer it

  \textbf{UTF-8 NFC LF no BOM}
\end{center}
